---
title: "R, y u do dis?"
author: Christoph Molnar
date: February 6, 2017
output: ryudodis_presentation
---

# Title slide

## For who is R the first programming language? Who started with something else?
# Some daily issues

## Machine numbers

## Non standard evaluation

## Implicit type conversions
example with matrix TRUE/FALSE
also problems with dply tbl, have to cast to data.frame

## NA behaviour


## Behaviour in special cases
all() and any()

## I loaded to packages, one overwrites a function of the other
Example part 1: 
```{r}
library('dplyr')
dat = read.csv('iris.csv')
dat %>% mutate(x_sqrt=sqrt(x)) %>% select()
```

ADD MEME

Example part 2:
```{r}
library('dplyr')
library('data.table')

dat = fread('table.csv')
dat %>% mutate(x_sqrt=sqrt(x)) %>% select()
```

ADD MEME

Gives Error
What happened?

## How to find the source code of a function
Often you want to know what is happening under the hood. Maybe you want to make a little adaption to the function. 
How can you find the code?
Often: Type the function in terminal
When package not loaded: 
Hidden function: Type :::
S3: method
S4: @
For C or Fortran functions: 

## NA behaviour for all(), any(), mean(), median(), ...


# Summary

## The good things about R

- Written by statisticians for statisticians (DSL?)
- Dynamic typing 
- S3 classes
- Non standard evaluation
- Language for creating DSLs (dplyr, ggplot, data.table, ...)
- package system 

## The bad things about R

Same as good things. 

## Tipps

- Do not overwrite base functions
- Do library('ggplot'), don't library(ggplot)
- 


